---
title: "STAT 107 Final Project—Final Report"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract
In Japanese, there are three main writing systems: Hiragana, Katakana, and Kanji. Hiragana and Katakana are both phonetic-based (i.e., every character represents a sound), while Kanji is pictorial (i.e., each character represents a concept). While each writing system represents the same set of sounds, for individuals learning how to read in Japanese, it is often confusing to know which writing system to learn first. Should an individual's goal in learning Japanese be to read novels, it is interesting to know what writing system one would encounter the most—as to most efficiently tailor their learning experience to meet their goals. 

Thus, we plan to sample 20 books from the online sources Gutenberg and Aozora websites to determine the overall distribution of Hiragana, Katakana, and Kanji within them. 


## Part 1: Data 

### Part 1.1: Japanese Literature

For this project, we will observe several novels from both the Gutenberg[www.gutenberg.org] website and the Aozora[https://www.aozora.gr.jp/.] website. We chose these sites due to the types of literature within them. From what we observed, the Japanese selection on Gutenberg mostly consists of works translated TO Japanese, while Aozora mostly consists of works written ORIGINALLY in Japanese. Thus, collecting a sample from both of the sites can provide insights as to how the distribution of each of the three writings systems differ between originally-Japanese works and works translated to Japanese. 

We randomly selected 10 novels from both websites. However, this was done differently for both websites. For the noveles on the Gutenberg website, a simple random selection of all the Japanese language books on the site was conducted.
However, this was not necessairly possible on Aozora—as the only way to see a masterlist of all of the novels is through sorting by authors. Thus, we ran a SRS on the authors that are not under copyright, and randomly select one of their novels (if they have multiple novels listed under their authorship).

The novels we ended up selecting  (and their file names) are the following: 

From Gutenberg:

1. ("pg36358.txt")  お目出たき人 by Saneatsu Mushanokoji: https://www.gutenberg.org/ebooks/31757

2. ("pg37605.txt")  羹 by Jun'ichiro Tanizaki: https://www.gutenberg.org/ebooks/36459

3. ("pg34084.txt")  幽霊書店 by Christopher Morley: https://www.gutenberg.org/ebooks/41325

4. ("pg37626.txt")  下宿人 by Marie Belloc Lowndes: https://www.gutenberg.org/ebooks/32978

5. ("pg31757.txt")  友情 by Saneatsu Mushanokoji: https://www.gutenberg.org/ebooks/33307

6. ("pg36459.txt")  刺靑 by Jun'ichiro Tanizaki: https://www.gutenberg.org/ebooks/31617

7. ("pg41325.txt")  火星の記憶 by Raymond F. Jones: https://www.gutenberg.org/ebooks/36358

8. ("pg32978.txt")  惡魔 by Jun'ichiro Tanizaki: https://www.gutenberg.org/ebooks/37605

9. ("pg33307.txt")  法螺男爵旅土産 by Kuni Sasaki: https://www.gutenberg.org/ebooks/34084

10. ("pg31617.txt") 續惡魔 by Jun'ichiro Tanizaki: https://www.gutenberg.org/ebooks/37626


From Aozora:

1. ("onnano_kao.txt")                 人間の本性 by Shin, Katakami: https://www.aozora.gr.jp/cards/000492/card42252.html

2. ("ningenno_honsho.txt")            化学改革の大略 by Shimizu, Usaburo: https://www.aozora.gr.jp/cards/001508/card51403.html

3. ("kagaku_kaikakuno_tairyaku.txt")  枯尾花 by Sekine, Mokuan: https://www.aozora.gr.jp/cards/001358/card49253.html

4. ("kareobana.txt")                  将棋の話 by Shigeru, Tonomura: https://www.aozora.gr.jp/cards/001499/card52185.html

5. ("shogino_hanashi.txt")            色盲検査表の話 by Shinobu, Ishihara: https://www.aozora.gr.jp/cards/001742/card55751.html

6. ("shikimo_kensahyo.txt")           父八雲を語る by Iwao, Inagaki: https://www.aozora.gr.jp/cards/001961/card58832.html

7. ("chichi_yakumoo_kataru.txt")      おくのほそ道 by Matsuo, Basho: https://www.aozora.gr.jp/cards/002240/card61619.html

8. ("02okunohosomichi.txt")           青バスの女 by Tatsuno, Kyushi: https://www.aozora.gr.jp/cards/001782/card56514.html

9. ("ao_basuno_onna.txt")             古事記物語 by Otomo, Yasumaro: https://www.aozora.gr.jp/cards/000107/card1530.html

10. ("kojiki_monogatari.txt")         女の顔 by Kuroda, Seiki: https://www.aozora.gr.jp/cards/000257/card1425.html


### Part 1.2: Dataframe

After cleaning the data and processing it (see "Part 2: Data Cleaning/Processing"), we end up with a single dataframe called `jp_novels_df`—of which contains the following variables:

1. `site`: factor. A variable describing which of the two sites (Gutenberg or Aozora) the novel came from.

2. `body_chars_total`: numerical. Total number of characters in the actual text of the literature (excluding the characters found in the header/footer).

3. `kanji`: numerical. Total number of characters from the body that are in Kanji.

4. `hiragana`: numerical. Total number of characters from the body that are in Hiragana.

5. `katakana`: numerical. Total number of characters from the body that are in Katakana.

6. `japanese_total`: numerical. Total number of characters from the body that are in Japanese (`kanji` + `hiragana` + `katakana`).

7. `non_japanese`: numerical. Total number of characters from the body that are NOT in Japanese.

8. `removed_chars_header_footer`: numerical. Number of characters removed from the novel file as part of the header/footer.

9. `removed_ascii_english`: numerical. Number of Latin-script characters (ie, characters in English) that was removed from the novel file. 

## Part 2: Data Cleaning/Processing

```{r}
jp_novel_df <- data.frame()
```


## Part X: Team Member Contributions:
1. Pankshi Parekar: Created/Organized the GitHub repository. Created/Organized the Final Report. Wrote the Abstract, as well as parts 1.1, 1.2, in the report. 

2. Isabella Perez: 

3. Ulices Ramirez Lopez: 
