---
title: "T-Test: Aozora vs. Gutenberg (Total Characters)"
output: html_document
date: "2025-12-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document performs a two-sample t-test comparing the total number of characters in novels from Aozora website and the Project Gutenberg website. 

Our goal is to see whether the mean total character count per novel differs between two coursed.

#Pre-Test Screening
Before running a two-sample t-test, we check the usual assumptions:
1. Independence: 
Each row in our dataset represents a different novel, so it is reasonable to assume independence. 
2. Approximately Normal Distribution:
Total character counts may not be perfectly normal, but t-tests are robust with samples of this size
3. Equal or Unequal Variances
R's default t-test does not assume equal variances
We will:
- Look at sample variances
- Run var.test()
- Proceed with the Welch t-test
```{r}
# Load data 
aozora_df    <- read.csv("aozora_summary.csv")
gutenberg_df <- read.csv("gutenberg_summary.csv")

# Extract the variable we are comparing
aozora_chars    <- aozora_df$body_chars_total
gutenberg_chars <- gutenberg_df$body_chars_total

summary(aozora_chars)
summary(gutenberg_chars)

var(aozora_chars)
var(gutenberg_chars)

```
Because the sample variances for Aozora and Gutenberg differ substantially (Aozora ≈ 9.35×10⁸ characters² vs. Gutenberg ≈ 5.17×10⁹ characters²), the equal-variance assumption is not satisfied. However, since Welch’s two-sample t-test does not require equal variances and each novel represents an independent observation, it is still appropriate to proceed with the test. Additionally, while total character counts may not be perfectly normal, the t-test is robust enough for these sample sizes.

#Two-Sample T-Test
Now we test:
Null hypothesis: The mean total number of characters per novel is the same for Aozora and Gutenberg.
Alternative Hypothesis: The means are different.
```{r}
t_result <- t.test(
  aozora_chars,
  gutenberg_chars,
  alternative = "two.sided",
  mu = 0,
  conf.level = 0.95
)

t_result

# Group means for interpretation
mean_aozora    <- mean(aozora_chars)
mean_gutenberg <- mean(gutenberg_chars)

mean_aozora
mean_gutenberg

```
Result:
- Mean (Aozora): 17670.8
- Mean (Gutenberg): 113813.2
- 95% Confidence Interval: [-149882.97, -42401.83]
- p-value: 0.00209



