---
title: "T-Test: Aozroa vs Gutenberg (Writing Systems)"
output: html_document
date: "2025-12-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document performs three two-sample t-tests comparing the number of Hiragana, Katakana, and Kanji characters between novels from Aozora website and the Project Gutenberg website.

Our goal is to determine whethet the mean count of each writing system differs between the two sources.

# Pre-Test Screening
Before running each two-sample t-test, we check the usual assumptions:

1. Independence
   Each row represents a different novel, so the observations are independent.

2. Approximately Normal Distribution 
   Raw writing-system counts may not be perfectly normal, but Welch’s t-test is robust for small sample sizes.

3. Equal or Unequal Variances  
   Writing-system counts may differ greatly in variance between Aozora and Gutenberg. Since Welch’s t-test does not assume equal variances, it is appropriate for these comparisons.
   
```{r}
aozora_df    <- read.csv("aozora_summary.csv")
gutenberg_df <- read.csv("gutenberg_summary.csv")

# Extract writing-system counts
aozora_hira    <- aozora_df$hiragana
gutenberg_hira <- gutenberg_df$hiragana

aozora_kata    <- aozora_df$katakana
gutenberg_kata <- gutenberg_df$katakana

aozora_kanji    <- aozora_df$kanji
gutenberg_kanji <- gutenberg_df$kanji

# Summaries and variances
summary(aozora_hira); summary(gutenberg_hira)
var(aozora_hira);     var(gutenberg_hira)

summary(aozora_kata); summary(gutenberg_kata)
var(aozora_kata);     var(gutenberg_kata)

summary(aozora_kanji); summary(gutenberg_kanji)
var(aozora_kanji);     var(gutenberg_kanji)
```

The variances for Hiragana, Katakana, and Kanji all differ greatly between Aozora and Gutenberg, meaning the equal-variance assumption is not met. However, since Welch’s t-test does not require equal variances and the observations are independent, it is still appropriate to proceed. Although the distributions may not be perfectly normal, the t-test is robust enough for our sample size.

# Test 1: Hiragana 
- Null hypothesis: The mean number of Hiragana characters is the same for Aozora and Gutenberg.  
- Alternative hypothesis: The means differ.

```{r}
hira_result <- t.test(
  aozora_hira,
  gutenberg_hira,
  alternative = "two.sided",
  mu = 0,
  conf.level = 0.95
)

hira_result

mean_aozora_hira    <- mean(aozora_hira)
mean_gutenberg_hira <- mean(gutenberg_hira)

mean_aozora_hira
mean_gutenberg_hira
```
Result:
Mean (Aozora Hiragana): 11,958.7
Mean (Gutenberg Hiragana): 64,849.6
95% Confidence Interval: -90772.34,−15009.46
p-value: 0.009965

# Test 2: Katakana
- Null hypothesis: The mean number of Katakana characters is the same for Aozora and Gutenberg.  
- Alternative hypothesis: The means differ

```{r}
kata_result <- t.test(
  aozora_kata,
  gutenberg_kata,
  alternative = "two.sided",
  mu = 0,
  conf.level = 0.95
)

kata_result

mean_aozora_kata    <- mean(aozora_kata)
mean_gutenberg_kata <- mean(gutenberg_kata)

mean_aozora_kata
mean_gutenberg_kata
```
Result:
Mean (Aozora Katakana): 1,446.7
Mean (Gutenberg Katakana): 15,947.7
95% Confidence Interval: −25882.305,−3119.695
p-value: 0.01792

# Test 3: Kanji
- Null hypothesis: The mean number of Kanji characters is the same for Aozora and Gutenberg.  
- Alternative hypothesis: The means differ,
```{r}
kanji_result <- t.test(
  aozora_kanji,
  gutenberg_kanji,
  alternative = "two.sided",
  mu = 0,
  conf.level = 0.95
)

kanji_result

mean_aozora_kanji    <- mean(aozora_kanji)
mean_gutenberg_kanji <- mean(gutenberg_kanji)

mean_aozora_kanji
mean_gutenberg_kanji

```
Result:
Mean (Aozora Kanji): 6,277.2
Mean (Gutenberg Kanji): 32,547.3
95% Confidence Interval: −44220.753,−8319.447
p-value: 0.007955