---
title: "Graphs for Preliminary Analysis"
output: html_notebook
---

This file is meant to generate the graphs/figures seen within the Data Cleaning/Preliminary Analysis sections (Parts 1-3) of the Final Project Report. 

# Figure 0: jp_novels_df

```{r fig0, echo=FALSE}
library(ggplot2)

jp_novels_df <- read.csv("../Data Processing/jp_novels.csv")
  
head(jp_novels_df, 10)
```



# Figure 1: Raw Distributions of Hiragana, Katakana, and Kanji

```{r fig1, echo=FALSE}
# [NOTE]: Figure 1

par(mfrow = c(1, 3))

boxplot(jp_novels_df$hiragana, main = "Hiragana Distribution", 
        ylim = c(0, 150000), col = rgb(1, 0, 0, 0.25))
boxplot(jp_novels_df$katakana, main = "Katakana Distribution",  sub = "Figure 1",
        ylim = c(0, 150000), col = rgb(0, 1, 0, 0.25))
boxplot(jp_novels_df$kanji, main = "Kanji Distribution", 
        ylim = c(0, 150000), col = rgb(0, 0, 1, 0.25))
```


# Figure 2: Proportional Distributions of Hiragana, Katakana, and Kanji

```{r fig2, echo=FALSE}
# [NOTE]: Figure 2

# [STEP 1]: Create a new column in `jp_novels_df` that represents the proportion of each novel's Japanese characters that are part of a given writing system.
jp_novels_df$hiragana_proportion <- jp_novels_df$hiragana / jp_novels_df$japanese_total
jp_novels_df$katakana_proportion <- jp_novels_df$katakana / jp_novels_df$japanese_total
jp_novels_df$kanji_proportion <- jp_novels_df$kanji / jp_novels_df$japanese_total

# [STEP 2]: Display 
par(mfrow = c(1, 3))

boxplot(jp_novels_df$hiragana_proportion, 
        main = "Hiragana Proportion Distribution",
        cex.main = 0.9,
        ylim = c(0, 1), col = rgb(1, 0, 0, 0.25))
boxplot(jp_novels_df$katakana_proportion, 
        main = "Katakana Proportion Distribution",  sub = "Figure 2",
        cex.main = 0.9,
        ylim = c(0, 1), col = rgb(0, 1, 0, 0.25))
boxplot(jp_novels_df$kanji_proportion, 
        main = "Kanji Proportion Distribution", 
        cex.main = 0.9,
        ylim = c(0, 1), col = rgb(0, 0, 1, 0.25))

```



# Figures 3 to 5: Distribution of Japanese Writig Systems in Japanese Novels, Split by Host Website

```{r fig3-fig5, echo=FALSE}
# [NOTE]: Figures 3 through 5

ggplot(jp_novels_df, aes(x = hiragana_proportion)) + 
  geom_boxplot(aes(col = site)) + xlim(0, 0.8) + 
  ggtitle("Distribution of Hiragana in Japanese Novels, Split by Host Website",
          subtitle = "Figure 3") + 
  xlab("Proportion of Novel")

ggplot(jp_novels_df, aes(x = katakana_proportion)) + 
  geom_boxplot(aes(col = site)) + xlim(0, 0.8) +
  ggtitle("Distribution of Katakana in Japanese Novels, Split by Host Website",
          subtitle = "Figure 4") +
  xlab("Proportion of Novel")

ggplot(jp_novels_df, aes(x = kanji_proportion)) + 
  geom_boxplot(aes(col = site)) + xlim(0, 0.8) +
  ggtitle("Distribition of Kanji in Japanese Novels, Split by Host Website",
          subtitle = "Figure 5") +
  xlab("Proportion of Novel")

```


